### 2014-10-23 paper/include/rioparis.tex
dtail addition

As mentioned earlier, RIO and PARIS can be combined, which results in PARIS removing unnecessary refreshes and RIO lowering the rate at which the performed refreshes are done. This is similar to what Cui et al. does with DTail-RV. Cui et al. manages to lower the number of refreshes somewhat more than Baek et al. does with RIO and PARIS. The difference comes from DTail-V performing better than PARIS due to DTail keeping Validity information per row instead of per group of rows. RIO and DTail-R performs similar but RIO have a bigger storage overhead. DTail requires changes to the MC while RIO and PARIS is implemented in software and thus are more easy to realize.

>>>>

As mentioned earlier, RIO and PARIS can be combined, which results in PARIS removing unnecessary refreshes and RIO lowering the rate at which the performed refreshes are done. This is similar to what Cui et al. does with DTail-RV. Cui et al. manages to lower the number of refreshes somewhat more than Baek et al. does with RIO and PARIS. The difference comes from DTail-V performing better than PARIS both due to DTail keeping Validity information per row instead of per group of rows, and that DTail switches between CBR and ROR which PARIS does not do. RIO and DTail-R performs similar but RIO have a bigger storage overhead. DTail requires changes to the MC while RIO and PARIS is implemented in software and thus are more easy to realize.
